### 2023-02-13 main.qmd
Create misc folder
Remove .Rprofile

# Load custom helper functions
source(here("manuscript_files", "helper_functions.R"))

@@

# Options for MCMC sampling when fitting Bayesian multilevel models
n_iter <- 20000 # Posterior samples per chain, including `n_warmup`
n_warmup <- 2000 # Warmup samples per chain
n_chains <- 4 # Number of (parallel) chains
seed <- 1234 # Random seed to make the results reproducible

>>>>

# Load custom helper functions
source(here("misc", "helper_functions.R"))

@@

# Options for MCMC sampling when fitting Bayesian multilevel models
options(brms.backend = "cmdstanr") # Can choose "rstan" instead
options(mc.cores = parallel::detectCores()) # Use all available cores
n_iter <- 20000 # Posterior samples per chain, including `n_warmup`
n_warmup <- 2000 # Warmup samples per chain
n_chains <- 4 # Number of (parallel) chains
seed <- 1234 # Random seed to make the results reproducible
